---
title: 'Using NLP to Predict Michelin'
author: "Lester"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: no
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
#
rm(list = ls())
graphics.off()

# knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(
  collapse=FALSE,
  comment="#",
  message=FALSE,
  warning=FALSE,
  cache=TRUE,
  cache=FALSE,
  fig.align = "center"
)

path_root="."
# path_figs=file.path(path_root, "figures")
# path_libs=file.path(path_root, "libs")
# if (FALSE){source(file.path(path_libs, "run.R"))}
```

# About Project
In this project, we are interested to predict which restuarants will have a Michelin-star by using online reviews (unstructured data) and other structured data.

We will be covering the following content:

1. Data Pre-Processing, Tokenization
2. Topic Modelling (LDA)
3. Word Embedding (Word2Vec, GLoVe)
4. Predictive Modelling (randomForest)

Project Reference:
https://www.theanalyticslab.nl/nlpblogs_0_preparing_restaurant_review_data_for_nlp_and_predictive_modeling/
https://www.theanalyticslab.nl/nlpblogs_1_identifying_topics_using_topic_-modeling_lda/
https://www.theanalyticslab.nl/nlpblogs_2_training_word_embedding_models_and_visualize_results/
https://www.theanalyticslab.nl/nlpblogs_3_use_topic_modeling_results_in_predictive_modeling/



# Article 2


Import Data
```{r}
# **reviews.csv**: a csv file with review texts - the fuel for our NLP analyses. (included key: restoreviewid, hence the unique identifier for a review) 
reviews <- read.csv(file = 'data/reviews.csv',header=TRUE,stringsAsFactors=FALSE)

# **labels.csv**: a csv file with 1 / 0 values, indicating whether the review is a review for a Michelin restaurant or not (included key: restoreviewid)
labels <- read.csv(file = 'data/labels.csv',header=TRUE,stringsAsFactors=FALSE)

# **restoid.csv**: a csv file with restaurant id's, to be able to determine which reviews belong to which restaurant (included key: restoreviewid)
restoids <- read.csv(file = 'data/restoid.csv',header=TRUE,stringsAsFactors=FALSE)

# **trainids.csv**: a csv file with 1 / 0 values, indicating whether the review should be used for training or testing - we already split the reviews in train/test to enable reuse of the same samples for fair comparisons between techniques (included key: restoreviewid)storage_download(cont, "blogfiles/labels.csv",overwrite =TRUE)
trainids <- read.csv(file = 'data/trainids.csv',header=TRUE,stringsAsFactors=FALSE)

# **features.csv**: a csv file with other features regarding the reviews (included key: restoreviewid)
features <- read.csv(file = 'data/features.csv',header=TRUE,stringsAsFactors=FALSE)
```







